\section{Acknowledgements}

We would like to express our thanks to our supervisors, David Tarrant and Les Carr, whose guidance has been extremely valuable throughout this project. We would like to thank David Tarrant for his input and suggestions during meetings and ongoing feedback, as well as providing us with the necessary resources to work on this project.

We would also like the thank to Peter Wood and Nick Culley from Inqb8r, developers of Project4, who have ensured that required resources were in place for the duration of the project. Special thanks in particular to Peter Wood, whose great enthusiasm for this project has motivated our interest in the project and whose knowledge in the area of live streaming has greatly informed our product's design.

We'd like to extend thanks to VisualDNA for their support of this project, and their offer to provide assistance and mentioning. We would particularly like to thank the CTO of VisualDNA, Tomas Cervenka, for his interest in the outcome of this project and his commitment to extend it further.

Finally, we wish to thank those behind the following projects:
\begin{enumerate}
\item Atlas API\footnote{Atlas API -- \footurl{http://atlasapi.org}} -- a REST service for accessing EPG and programme data. Thanks to MetaBroadcast\footnote{MetaBroadcast website -- \footurl{http://metabroadcast.com}}, in particular Jonathan Tweed, who have provided us with access to this. This data is in turn provided by Press Association\footnote{Press Association website -- \footurl{http://www.pressassociation.com}}.
\item MovieLens\footnote{MoveLens -- \footurl{http://movielens.umn.edu}} -- rating and demographic data, which were used to train the recommendation system. Thanks to GroupLens research.
\item TheTVDB\footnote{TheTVDB -- \footurl{http://thetvdb.com}} -- an API to programatically find the genres of movies, which was used for classifying new programmes by the recommender.
\end{enumerate}

\cleardoublepage
\setcounter{tocdepth}{2}

\begin{comment}
	\tableofcontents
	\newpage
	\cleardoublepage
	\setcounter{page}{0}
	\pagenumbering{arabic}
	\cleardoublepage
\end{comment}

