\section{Implementation}

\subsection{Languages and Techniques}
As this project involved interacting with many different systems, a diverse range of programming languages were used.

\subsubsection{Client-side web interfaces}
\begin{enumerate}
\item \textit{HTML}
\item \textit{CSS}
\item \textit{JavaScript}
\end{enumerate}

\subsubsection{Server-side and data-layer}
\begin{enumerate}
\item \textit{PHP}
\item \textit{Python}
\end{enumerate}

Communication between server and client is done through a REST interface.

Datebase is MySQL.

\subsubsection{Streaming server}
\begin{enumerate}
\item \textit{Java} to interface with the Wowza streaming server
\item \textit{Python} to interpret to GPI[?] pulse in order to establish when breaks in live programmes are
\end{enumerate}

\subsection{Libraries and Frameworks}

\subsection{Detailed Architecture}

\subsubsection{Database structure}

\subsubsection{Programme recommendation}

\subsubsection{Advert selection}

\subsubsection{REST services}

\subsubsection{Playback}
Plays HLS streams in HTML5 Video tag, or RTMP stream in Flash Video.

The player must be capable of displaying two types of media: \textit{video} (for programmes and video adverts) and \textit{stills} (for adverts which consist of just one picture). Additionally, some adverts may have an overlay, which consists of some HTML specified by the advertiser. A challenge here is hiding the buffering of videos or loading of images. A solution is to hide any media until it has loaded. Layers:
\begin{enumerate}
\item \textit{Black layer}: used to hide any loading media
\item \textit{Overlay layer}: an iFrame which will display the HTML that the advertiser has specified for the overlay
\item \textit{Still layer}: an image that will display any still adverts
\item \textit{Video layer}: the video component to show the video
\end{enumerate}

\subsubsection{Data visualisation}


\subsection{Code Statistics}
Lines of code in JS, PHP, Java, Python, HTML, CSS etc


