\section{Interviewer Script}
\label{sec:appendix_interview_script}

Below is the script that a researcher would read to participants during the user study (see Section~\ref{sec:user_study}).

\begin{quotation}
	\noindent Hi.

	Thank you for agreeing to participate in our study - this should not take more than half an hour. In a moment you will be given an iPad, which will show you a short video to introduce you to the rest of the study.

	Do you have any other questions before we begin?\\

	\noindent $\langle$Participant watches introductory video and two rounds of adverts, as scripted in Appendix~\ref{sec:appendix_video_script}.$\rangle$\\

	\noindent I'd like to emphasise that this is not a test: we are just interested in seeing what your impressions were and how much you remember.\\

	\begin{enumerate}
		\item What were the adverts you just watched about? \\
			Describe what happened and what they were advertising in as much detail as you can.\\
	\end{enumerate}

	\noindent You've just watched two streams -- one with some interactive adverts, and one without any. [Swap order as appropriate]\\

	\begin{enumerate}
	  	\setcounter{enumi}{1}
		\item How long do you believe you were watching each stream?\\
			$\langle$Optional prompts (if they mention that one session was longer):$\rangle$
		\begin{enumerate}[label=\alph*]
			\item Were you watching the [first/second] round for a much longer period, a little longer, the same amount of time, a little less or a lot less?
			\item Please estimate how much time more or less you were watching in the [first/second] session?
		\end{enumerate}

		\item Did you pay more attention to adverts that were relevant to you?
		\item During which session did you pay more attention to adverts (if either)?
		\item During which session do you remember more about the adverts shown (if either)?
		\item Which session did you enjoy more - interactive or passive?
		\item If you were able to choose, which system would you prefer to be used for live streaming media on iPads, and why?
		\item I'm now going to ask you some questions specifically about the interactive adverts, in the [first/second] session.
		\begin{enumerate}[label=\alph*]
			\item Which adverts had interactive elements (if any) and what were they?
			\item Which adverts did you interact with and why did you choose to interact with them specifically at that time?
			\item You saw some of the adverts twice - once with an interactive overlay, and once without. Did you prefer the adverts with an interactive element to them?
			\item Were you able to easily work out how to interact with an advert?
			\item Of the interactive adverts, which advert(s) did you like best and why?\\
		\end{enumerate}
	\end{enumerate}

	\noindent Last few questions:\\

	\begin{enumerate}
	  	\setcounter{enumi}{8}
		\item Do you believe that if adverts were more relevant to you, you would watch them more often?\\
	\end{enumerate}

	\noindent There are multiple pieces of information that can be used to target adverts (make them more relevant). I'm going to mention a number of categories, and I'd like you to tell me how comfortable you are with the use of that information for advertisement targeting.\\

	\begin{enumerate}
	  	\setcounter{enumi}{9}
		\item What levels of targeting would you be comfortable with in these categories:
		\begin{enumerate}[label=\alph*]
			\item Demographics (anonymous information about age, gender and occupation),
			\item Your current location,
			\item The time you watch the advert (e.g. lunchtime, late evening),
			\item The context you watch the advert in (e.g. the programme you’ve just watched/are watching/are about to watch),
			\item Internet browsing history,
			\item Significant changes to information on Facebook (e.g. relationship status changing, new occupation)
			and
			\item Information learned by the system from previous interaction (e.g. adverts you've clicked on before, programmes you've chosen)\\
		\end{enumerate}
	\end{enumerate}

	\noindent Final question:\\

	\begin{enumerate}
	  	\setcounter{enumi}{10}
		\item Do you have any other comments, questions or comparisons about the two systems you've used today, or any other advertising systems that you know of?\\
	\end{enumerate}

	\noindent Thank you for participating in our study.
\end{quotation}