\section{Video Script}
	\label{sec:appendix_video_script}
	Hi,\\
	Thanks for volunteering for this study. In this study, we want to find out a bit more about how people view TV adverts. 

	We're about to show you two sets of adverts. After these, we'll ask you a series of questions on your experience.

	We ask that during this study you remain focused on the screen, and don’t communicate with the researcher unless there is a problem, and please don’t use your phone or other devices.

	When you're ready to begin, press `Start'. If you would like to watch this introduction again, press `Replay'.

	$\langle$The participant is then shown the introduction for whichever is their first round.$\rangle$

	$\langle$The participant is then shown the introduction for the remaining round.$\rangle$

	[Round introduction: Passive]

	The adverts you're about to be shown are adverts as you might see on TV. All you need to do is watch these adverts and we'll ask you some questions about your experience at the end of the study.

	Press `Start' to begin. Press `Replay' to watch these instructions again.

	[Round introduction: Interactive]

	In this round, you will be shown adverts as you might be shown adverts on TV, except some adverts will allow you to interact with them. During this round, you should watch the adverts, and you may also wish to tap or swipe the screen in order to interact with adverts that allow you to. 

	You can touch the screen in order to interact with parts of these adverts. We'll ask you some questions about your experience with these adverts at the end of the study.

	Press `Start' to begin. Press `Replay' to watch these instructions again.
	
	$\langle$Once both rounds are over, the participant is shown the closing segment.$\rangle$

	[Final segment]

	Thank for participating in the experiment. The researcher will now ask you a series of questions about your experiences. Try to answer honestly and as completely as possible. Do not be afraid to ask for clarification if you do not understand a question.

	[END]
